---
title: "Count Data Analysis"
---

We use the function glm( ) to run the Poisson log linear model regression

log(λit )= β0 + β1×Discount + β2×Target + β3×Income+ β4×Distant + β5×Gender 

```{r}
mv.data <- read.csv("Mall_visit.csv")
```
```{r}
mv.re1= glm(Visit~Discount+Target+Income+Distant+Gender, data=mv.data, family = poisson)
summary(mv.re1)
```
```{r}
AIC(mv.re1)
BIC(mv.re1)
```

Firstly, we transform the customer ID from integers into factors (levels). 

According to the summary(), the coefficient of Target, B2 ，is not significant. 



Next, we will allow each individual customer to have a different intercept  

Log(λit )= β0i + β1×Discount + β2×Target + β3×Income+ β4×Distant + β5×Gender, 

where the individual intercept β0i will be a random effect (500 of them) grouped by customerID.

```{r}
mv.re2= glmer(Visit~Discount+Target+Income+Distant+Gender+(1|customerID), data=mv.data, family = poisson)
summary(mv.re2)
```
```{r}
AIC(mv.re2)
BIC(mv.re2)
```

We will also fit the negative binomial model for the count data.  Let the mean of the negative binomial distribution be

log(λit )= β0 + β1×Discount + β2×Target + β3×Income+ β4×Distant + β5×Gender

```{r}
mv.re3= glm.nb(Visit~Discount+Target+Income+Distant+Gender, data=mv.data)
summary(mv.re3)

```
```{r}
AIC(mv.re3)
BIC(mv.re3)
```
According to the summary(), the coefficient of Target，B2 ，is not significant. 

Based on the AIC/BIC above, the second regression (Poisson linear model with random effect) is best model for the data.

```{r}
mv.re4= MCMChpoisson(Visit~Discount+Target+Income+Distant+Gender, random=~1,group = "customerID", data=mv.data, burnin = 10000, mcmc = 20000, thin = 20,r = 2,R=diag(1))
summary(mv.re4$mcmc[,1:6])
```
All the coefficients are significant. 
